---
title: "XinqianDai PS6"
author: "Xinqian Dai"
date: "4/8/2022"
output: pdf_document
---
```{r}
library(alr4)
fit <- lm(lifeExpF~group+fertility+ppgdp+pctUrban,data=UN11,x=T)
X.mat <- fit$x
H <- X.mat%*%solve(t(X.mat)%*%X.mat)%*%t(X.mat) 
h <- diag(H)
p <- dim(X.mat)[2]
n <- dim(UN11)[1]
# studentized residual:
sigma.hat <- summary(fit)$sigma
r <- resid(fit)/(sigma.hat*sqrt(1-h))
# studentized deleted residual (book eq 9.19)
t <- r*sqrt((n-p)/(n-p+1-r^2))
```

#1
```{r}
plot(fit,which=3)
plot(x = fitted(fit), y = sqrt(abs(t)))
```
#2
```{r}
UN11$row_num <- seq.int(nrow(UN11))
no.outlier <- UN11[-c(24, 101, 125), ]
myfit <- cooks.distance(fit)
sort(myfit)
```
The potential outliers from #1 are Lesotho, Botswana, and Nauru. They have the largest cook's distance.
```{r}
fit <- lm(lifeExpF~group+fertility+ppgdp+pctUrban,data=UN11,x=T)
plot(fit)
summary(fit)
```

```{r}
no.outlier.fit<-lm(lifeExpF~group+fertility+ppgdp+pctUrban,data=no.outlier,x=T)
summary(no.outlier.fit)
plot(no.outlier.fit)
```
According to  summary(fit) and summary(no.outlier.fit), the estimate of groupafrica changes a lot from -1.039e+01 to -9.542e+00 after removing the outliers.
Also, the p value of ppgdp changes from 0.03992 to  0.065591> 0.05, which makes it insignificant. Therefore, the outliers change the estimated model substantially.

#3
```{r}
anova(fit)
```
Sum of squares = treatment sum of squares (SST) + sum of squares of the residual error (SSE). The column splits the total variation of lifeExpF into different sources of variation. 12563.0 is the amount of variation caused by group; 3170.9 is the additional amount of variation attributed to fertility after group is already in the model; 305.8  is the additional amount that ppgdp decreases SSE by after group and fertilizer is already in the model;189.9 is the additional amount that pctUrban decreases SSE by after group, fertilizer, and ppgdp is already in the model. 4063.6 is the sum of squares of the residual error (SSE),

#4
```{r}
fit.intercept <-lm(lifeExpF~1, data=UN11) 
anova(fit,fit.intercept)
```
anova() shows a F value of 154.16 and p,2.2e-16, which are the same as the results in the last row of summary(fit). Since p<0.05, we reject the null hypothesis, and the full model is better.
