---
title: "XinqianDai PS5"
author: "Xinqian Dai"
date: "3/31/2022"
output: pdf_document
---

```{r}
library(alr4)
data <- data.frame(slim=Highway$slim,htype=Highway$htype,trks=Highway$trks,lograte=log(Highway$rate))
```

#1
```{r}
fit.1 <- lm(lograte~htype, data = data)
fit.2 <- lm(lograte~slim, data = data)
fit.3 <- lm(lograte~trks, data = data)
anova(fit.1)
anova(fit.2)
anova(fit.3)
```
SSR for highway type is 0.08727; SSR for speed limit is 3.8806; SSR for percentage of truck volume is 2.1966. 
The model with speed limit has the largest SSR and the smallest SSE, so speed limit matters the most for predicting the accident rate.

#2
```{r}
fit.interact<-lm(lograte~.^2,data=data)
fit.add<-lm(lograte~.,data=data)
summary(fit.interact)
summary(fit.add)
anova(fit.interact,fit.add)
```
R^2 of interaction model is slightly larger than that of addition model since interaction model has more Betas, and P is 0.9652>0.05 in F-test so we should not reject the null hypothesis. Therefore, interaction model isn't worthy and the addition model is better.


#3
```{r}
fit.intercept <-lm(lograte~1, data = data)
anova(fit.interact,fit.intercept)
anova(fit.add,fit.intercept)
```
When comparing the interact model to the intercept-only model, p value is 0.001085<0.05 so we reject the null hypothesis. Therefore, the interact model model is more useful.
When comparing the addition model to the intercept-only model, p value is 4.201*10^(-6)<0.05 so we reject the null hypothesis. Therefore, the addition model is more useful.

#4
```{r}
confint(fit.add)
summary(fit.add)
```
O is in the confidence interval of htype, and the absolute values of t-values of htype are smaller than 1.96 (i.e. p-values> 0.05),so we cannot conclude the betas are not statistical significantly different from zero. 
Similarly, O is not in the confidence interval of slim and trks, and the absolute value of t-values of slim and trks are larger than 1.96 (i.e. p-values< 0.05), which means that their betas are statistical significantly different from zero.

Therefore, slim(speed limit) and trks(truks) are statistically significantly related to the log accident rate.

#5
Use the three simple linear regression models from question1.
```{r}
summary(fit.1)
summary(fit.2)
summary(fit.3)
summary(fit.add)
```
Since the variability is represented by R^2,
from the three linear regression models in question1,
0.1072 variability in log rate is explained by htype,
0.4765 variability in log rate is explained by slim,
0.2697 variability in log rate is explained by trks.

From the addition model I chose from question2,
0.6146 variability in log rate is explained by the covariates.


#Extra Credit
```{r}
newinteract<-lm(lograte~trks*slim,data=data)
anova(newinteract,fit.add)
newadditive<-lm(lograte~trks+slim,data=data)
anova(newadditive,fit.add)
anova(newinteract,newadditive)
```
Since the highway type is not statistically significant, I remove highway type from both the addition model and the interaction model.
With anova() to compare full additive model with reduced interaction and additive models, the p values are 0.3497(>0.05) and 0.5585(>0.05).Therefore, the full addition model is not necessary.
Then with anova() to compare reduced additive model with reduced interaction model, the p value is 0.558(>0.05). Therefore, the reduced interaction model is not necessary, and the reduced addition model is the best.

